\addchap{Abstract}
This project addresses challenges with data quality and availability at Swiss Post. The environment of postal services is highly heterogeneous due to many factors. This causes challenges in non-operative reporting, where all heterogeneity is brought into global reports, placing these differences into a homogeneous environment.
In this environment, both the hardware used at the operational level and the software at the reporting level are under constant change. These changes can break existing data pipelines and introduce new ways and tools of reporting. The goal of this project is to help maintain high user confidence in non-operative reporting. This is achieved by setting up rules for data quality checks and improving business and IT understanding of their respective needs in the field of data quality and availability. This topic is highly relevant to both business and IT, as it helps provide value across the entire service process.
To reach this goal, research into data availability and data quality checks is conducted. This supports an understanding of what these checks do and where they should be implemented. In order to better map the challenges, both the data lineage and the reporting pipeline are researched and documented.
As the main contribution towards this goal, the current data quality checks performed by the business are evaluated. This evaluation helps to ensure that business-critical values are captured in future automation. After capturing the current methods, the applied checks are translated into generalised rules and prepared for implementation.

With the main contributions of describing the data lineage and reporting pipeline, and providing a documented first use case, this project contributes to future work in data quality management. It creates a solid base for the implementation of the rules in a subsequent project and for further research. With the transparency provided, the steps towards reducing manual validation efforts are established. These will be further researched during the master’s thesis, which will lay the groundwork for additional automated data quality checks in the Swiss Post DWH.