\section{SMART goal 1, Setup of a improved DQM report}
In project one, the base work researching the reporting pipeline was performed. It provided the data lineage and described the underlying issues. With this data, an improved report was developed. Research was conducted regarding how to better highlight the relevant comparisions and help the users see the information even faster. Additionally the third party datasource which is still copied daily into a excel file recieved improvements. The file was moved to sharepoint and is now updated on change to \gls{AWSS3} where it is made available to \gls{athena}. In addition to that the data selected recieved a change in it's structure.

\subsection*{Update of data source}
The Excel was updated from beeing copied to a shared folder to sharepoint.
Sharepoint allowed to use an existing interface Sharepoint to AWS.

This allowed to use the same interface also for the existing report in SAC, this setup was however done by another member of the ASTV team

\subsection*{Setup of Power BI}
State that for Power BI a setup existed already. This setup had to be used, however also allowing to use all existing infrastructure. Benefitting from prework of the DWH LS OPS Team which defined. 

\subsubsection*{Setup}
This setup consists of already predefined templates defining areas such as reporting color groups, regions for filters, how permissions for the reports are handled.
Furthermore the setup included definitions how to deploy reports and how to handle the AWS Athena data sources. Thus the setup was conducted as defined by post.

\subsubsection*{Report Definition}
The setup of the report was initially overtaken from the analysed report in \gls{SAC}, this decision was taken as the data which had to be checked remained the same. Therefore also the method the business followed stayed the same, and the first tests to get the data into Power BI returned the data in the same way.


\subsubsection*{New View Athena}
While the data source remained largely the same, the data lineage changed slightly. Business and IT decided in late 2025 that the data should be consumed as a star schema to improve performance compared to the existing wide table. Consequently, the \gls{DQM} dashboard for message processing needed to follow this change in the data source. In order not to disturb the previous report, the data had to be gathered into a separate view in \gls{athena}. The separate view was also required in order to validate the new star schema infoblocks rather than those of the previous wide table. Thus, separating the views was necessary to maintain clean, high performing code.

Todo... link to the query..



\subsubsection*{Initial Data Setup}

Due to this report beeing the first one developed by the project team, the first tries were performed locally without deploying the report to \gls{microsoftFabric}. 
As such first report, the abundance of ways how to achieve e.g. links between datasources naturally lead to a report setup which performed some tasks double. Such as linking the two data sources using \gls{mQuery} and \gls{dax}.
Issues with the Setup of the report
I first built everything local
However this did not work online..
Had no proper Chain of checkins
Had to redo the setup,
But now deployed it more often to find out if eventually one specific issue renders the data non usable

\subsubsection*{Initial Data Setup}
Describe that first only 1 query
Then 2 queries and combine them...
However later with the aggregation table...
Another data source was to be added, the semantic model



\subsubsection*{New visuals to help faster visual data reception by stakeholders}
However decision taken to use 3 visuals
1 visual using trafic lights , green orange red, also using different colors
2 using a line chart to show eventual recuring or increasing issues
3 using the existing table view of SAC but reinforcing the data with the trafic lights same as the trafic light visual

\subsubsection*{Waiting for finishing of aggregation}
-> To Solution LandScape
Technical limits due to data amount
pragmatic setup aggregating some values 
while some details are only availale as direct query (slower)

\subsubsection*{Input from stakeholders}
Input from team...
You need to use a data model
You need to move measures into a measure table
You should have filters differently
Use a table for dates, link it to every other date
same for PLZ
-> Rendering the Joined Key PLZ+Date non Needed

\subsubsection*{Requirement to rebuild the data model}
If available show the changes to the data model

\subsubsection*{Final Version of the Report}
Show how the final version looks