\chapter{Project management}

The project management chapter summarises the environment of this project and how it is conducted. First, the teams in which the project staff is engaged are listed, allowing the reader to see the relevant surrounding teams. Second, the different methods for effort and task tracking are introduced, so that the project and progress management methods applied are understood, together with their reasoning. Third, the toolsets used by the different teams are described, which allows the variety of tools and their usage to be grasped. Fourth, time tracking is introduced and explained for transparency, while the tracked time is provided in the Annex. Finally, the risk management section describes the risks handled and the measures taken to counteract them.

\input{Projectmanagement_Teams}
\input{Projectmanagement_Method}
\input{Projectmanagement_Tools}
\section{Timetracking}
As part of the need for transparency and the ability to review the efforts committed to this project, time tracking was performed from the start to the end of this documentation. The tracked time was recorded in two separate ways. Work efforts carried out within Swiss Post were captured directly from the Swiss Post \gls{MIAR} system, noting only the time spent per day without further details on the specific tasks performed. This information was saved in an Excel file and marked as work effort.

Second, academic efforts committed to the project outside the Swiss Post context were recorded directly in an Excel file. For each work block, a separate entry was created. A block represents continuous work on project-related tasks, including short breaks; however, longer breaks, such as lunch, resulted in a new block being created. Excel was used because the Office suite was already in use for other purposes, and the information did not justify storage in a more complex database such as MariaDB. The tracked time is not intended for billing or performance measurement, nor is it used to assess milestone performance.


\input{Projectmanagement_Risk}