\section{S.M.A.R.T. goals}
\label{ResearchSmartGoals}
The Goals of this project are now defined here as “\gls{SmartGoals}”, as shown in the following list. They are all \textbf{S}pecific: the goal is clearly formulated; \textbf{M}easurable: there are measurable criteria defining when the goal is reached; \textbf{A}chievable: they are realistic given the available resources; \textbf{R}elevant: the goal is directly linked to the project’s success; and \textbf{T}ime-bound: there is a defined timeframe for achievement.


Mein Vorschlag

Ich würde Projekt 2 auf drei SMART Goals reduzieren.

Sie entsprechen genau dem tatsächlichen Inhalt deiner Arbeit.

SMART Goal 1 – Development of an improved DQM reporting solution

WHY: To improve the usability and maintainability of the existing DQM report while supporting the migration to the new reporting architecture.

By the end of the implementation phase, the existing DQM report shall be redesigned in Power BI using the new star schema data products and the updated reporting pipeline.

Success is measured by a functioning report that reproduces the required business information, is accepted by the responsible stakeholders, and is successfully connected to the new data sources.

SMART Goal 2 – Evaluation of a future DQM platform

WHY: To identify a suitable technological foundation for future enterprise-wide data quality management.

By the end of the evaluation phase, available DQM solutions shall be compared against the technical and organisational requirements identified within Swiss Post.

Success is measured by a documented comparison of the evaluated tools, including their strengths, limitations, and an evidence-based recommendation for future implementation.

SMART Goal 3 – Validation of the selected monitoring technology

WHY: To verify that the selected technology can support the implementation of automated data quality monitoring in future work.

By the end of the implementation phase, a proof of concept shall demonstrate that the selected monitoring solution can retrieve representative data, process the returned information, and provide a suitable basis for automated DQM checks.

Success is measured by the successful execution of the proof of concept, including documented test results and an assessment of its suitability for the subsequent Master Thesis.