\chapter{Results}

Todo
Write the results chapter


This is the key chapter that reflects on the initial goals, the work carried out to achieve the goals, and the degree to which they were achieved. This chapter is structured around each goal, and special attention is paid to the key learnings that will be useful for subsequent phases of this work.


\section{Introduction}
The results presented here are part of a structured process that began step by step with the research question and led to the solution architecture and its implementation. Before delving further into the results of this project, a brief reminder of its scope helps to maintain focus. The project supports the \textbf{D}ata \textbf{W}are\textbf{h}ouse of \textbf{L}ogistic \textbf{S}ervices \textbf{Op}eration\textbf{s} (\gls{DWHLSOPS}) with the goal of improving \gls{DA} and \gls{DQ} management by replacing manual checks performed by the business with automated checks executed by IT. Through this change, data about these checks can become more consistent and enable the business to monitor them more easily. To achieve this, the existing reporting pipeline from raw data to the final report had to be re-engineered and documented.



\section{Evaluation criteria}
First, a result is defined as every piece of information that helps the reader become familiar with the context of the work. Second, it includes all information that supports understanding of the methods used during the project. Third, it comprises the main goal of this work, the SMART goals and their results. While the supporting results help to understand the environment, only the SMART goal results are the effectively relevant results of this work.

These SMART goals have been defined in the research chapter at \ref{ResearchSmartGoals}:

\begin{itemize}
\item \textbf{1) Identification of initial data quality metrics}
\item \textbf{2) Investigation of IT systems for DQM metrics}
\item \textbf{3) Investigation of data lineage for metrics}
\item \textbf{4) Design and testing of an automated DQM algorithm}
\item \textbf{5) Implementation and validation of an automated DQM check}
\end{itemize}





\section{Summary}
With this chapter, the SMART goals defined in the research chapter have been analysed for completion. Two goals were completely fulfilled, two were partially fulfilled, and one was not achieved. The partially fulfilled second goal was limited due to time constraints related to project deadlines and highlights the importance of obtaining confirmations from external teams as early as possible. The goal without results points towards the need for more realistic planning, as the project concluded within the defined timelines while providing the foundation for implementing a DQM check, but without allowing sufficient time for the actual implementation. However, it is important to note that although the goals leading towards the implementation of the DQM rules were not fully realised, the results of this project serve as a solid basis for subsequent projects and the continuation towards the master’s thesis.


